---
Title: QMM ASSIGNMENT-2
Author: Prasanth Yethirajula
output:
  pdf_document: default
  html_document: default
---
Question 1:


**Decision Variables:**
\(x\) = Number of Collegiate backpacks to produce per week.
\(y\) = Number of Mini backpacks to produce per week.

**Objective Function:**
Maximize \(Z = 32x + 24y\)

**Constraints:**
1. Material constraint: \(3x + 2y \leq 5000\)
2. Sales forecast constraint for Collegiate: \(x \leq 1000\)
3. Sales forecast constraint for Mini: \(y \leq 1200\)
4. Labor constraint: \(45x + 40y \leq 35 \times 40 \times 60\)

**Non-negativity constraints:**
\(x \geq 0\)
\(y \geq 0\)

Linear Programming model as :
$$Max\hspace{.1cm}Z\hspace{.2cm}=\hspace{.2cm}32b_c+24b_m$$
#tried solving the problem using LP model by defining the coeficients and 
#installing lpsolve and using library lpsolve.
```{r}
# Load the lpSolve library
library(lpSolve)

# Define the objective coefficients
obj_coef <- c(32, 24)

# Define the constraint coefficients and types
const_coef <- matrix(c(3, 2, 45, 40), nrow = 2, byrow = TRUE)
const_dir <- c("<=", "<=")

# Define the right-hand side of constraints
rhs <- c(5000, 35 * 40 * 60)  # Material and labor constraints

# Create an LP model
lp_model <- lp("max", obj_coef, const_coef, const_dir, rhs)

# Add variable bounds as constraints
var_bounds <- matrix(c(0, 1000, 0, 1200), nrow = 2, byrow = TRUE)
colnames(var_bounds) <- c("Collegiate", "Mini")
rownames(var_bounds) <- c("Lower", "Upper")

# Add variable bounds as constraints
const_coef_bounds <- rbind(const_coef, diag(2))  # Adding bounds as constraints
const_dir_bounds <- c(const_dir, "<=", "<=")
rhs_bounds <- c(rhs, c(0, 1000, 0, 1200))

# Solve the LP problem
solution <- lp("max", obj_coef, const_coef_bounds, const_dir_bounds, rhs_bounds)

# Print the results
cat("Number of Collegiate backpacks to produce per week:", solution$solution[1], "\n")
cat("Number of Mini backpacks to produce per week:", solution$solution[2], "\n")
cat("Optimal profit:", solution$objval, "\n")

```


Question 2

```{r}
#defining the matrix to table
table=matrix(c(20,900,420,15,1200,360,12,750,300), nrow = 3, ncol = 3, byrow = TRUE)
#Assigning colnames and row names
colnames<-(c('Space Required', 'Sales Forecast(PerDay)', 'Profit'))
rownames<-(c('Large', 'Medium','Small'))
table
```

``` {r}
#Second matrix
table=matrix(c(750,900,450), nrow = 3, ncol = 1, byrow = TRUE)
#Assigning colnames and rownames
colnames<-(c('Excess Capacity Units/Day'))
rownames<-(c('Plant1', 'Plant2','Plant3'))
table
```
Suppose,
Assume Size of the large product $$=L$$
Assume Size of the medium product $$=M$$
Assume size of the small product $$=S$$
Plant1 is assignes as $$=P1$$
Plant2 is assignes as $$=P2$$
Plant3 is assignes as $$=P3$$

(a) Decision Variables for the problem:$$L,M,S,P1,P2\hspace{.1cm}and\hspace{.1cm}P3$$
(b) Objective Function:
$$Max\hspace{.1cm}Z\hspace{.1cm}=\hspace{.1cm}420(P1L+P2L+P3L)+360(P1M+P2M+P3M)+300(P1S+P2S+P3S)$$
(c) Constraints:
1. Storage capacity (sq ft.): $$20P1L+15P1M+12P1S\le13000$$
                              $$20P2L+15P2M+12P2S\le12000$$
                              $$20P3L+15P3M+12P3S\le5000$$
2. Excess Capacity Storage:   $$P1L+P1M+P1S\le750$$
                              $$P2L+P2M+P2S\le900$$
                              $$P3L+P3M+P3S\le450$$
3. Sales forecast per day for every product:
        For Large             $$P1L+P2L+P3L=900$$
        For Medium            $$P1M+P2M+P3M=1200$$
        For Small             $$P1S+P2S+P3S=750$$
4. Same Percentage of their excess capacity is being used:
                              $$1/750(P1L+P1M+P1S)=1/900(P2L+P2M+P2S)$$
                              $$1/750(P1L+P1M+P1S)=1/450(P3L+P3M+P3S)$$
5. Non-negativity:            $$L\ge0$$
                              $$M\ge0$$
                              $$S\ge0$$
                              $$P_1\ge0$$
                              $$P_2\ge0$$
                              $$P_3\ge0$$
